\documentclass[11pt,en,authoryear]{elegantpaper}

\title{ AI for Game Testing and Measurement}
\author{Wangzhihui Mei \\ 2019124044 6603385}
\institute{UOW-CCNU JI}

\date{\today}

\begin{document}

\maketitle

% \begin{abstract}
 
% \keywords{ Game AI, Template}
% \end{abstract}


\section{Introduction}
\noindent
Game Artificial Intelligence (GAI) has been developed into real Artificial Intelligence rather then pseudo AI based on predefined automatic program. The achievement of AlphaGo in 2005 indicated that AI techniques have made greate development, while the game industry benefit little from the technology development. There is still a lot of room for exploration. One of these directions is to help Players improve the game experience, such as new game modes between AI players and human players, more realistic NPCs, etc. Another important direction is to help game production improve efficiency, such as reducing the coding difficulty of rules and behavior trees, game testing, game level generation, etc. 
 
\noindent
In this article we focus on how AI improves the effectiveness and efficiency of game testing. 

\section{Problem Statement}
\noindent
The traditional game development and testing workflow has run efficiently for a long time, but still fail to meet the challenges of high-speed iterations in today's gaming industry.
When the scenario that needs to be tested in game contains more strategic content, the traditional testing method seems to be a little powerless. Conventional automated testing methods can only be used to ensure that the game can run normally, and can not reliably and efficiently test the playability of the game. Also, The game interface animation are quite stochastic and complex, which makes it hard for automated test as the testing program agents may become over complex and enormous. Some teams initially use some rule-based test cases or robot-assisted test work, but simple rules often fail to adequately test the game scene or even pass customs. Complex rules can incur huge maintenance costs. As the content of the game is constantly adjusted during development, it is ultimately necessary to rely on a relatively low-cost manual method to complete the test. Not only that, games with more complicated rules, such as card games and war chess games, will generate a huge amount of strategy combinations, and it is extremely difficult to effectively cover all scenes with human resources. The beta test before the game goes online is one of the important links before the game is officially launched. This work is completely dependent on the players involved. Limited by the level of participation in the test of players and a variety of subjective factors, not only the feedback cycle is long, the test benchmarks and results can basically only be judged by experience. In summary, there is a need for better game testing methods and tools. The widely used AI techniques can be applied in these works. More specifically, the following research questions need to be addressed:
\begin{itemize}
    \item What are the procedures of different types game testing?
    \item How to apply AI techniques to adequately complete the game testing task?
    \item What are the current industry practice in game testing based on AI?
\end{itemize}

\section{Objectives}
\noindent
The ultimate goal of the research is to develop an effective game-testing AI. Game-testing AI consists of modeling, algorithm, the main objective is to evaluate the effectiveness and advantages of game testing based on AI techniques. This includes evalutation of performance, validity and feasibility. Also analyses of models and architecture of AI game-testing agents will be conducted, then the final report. 

With the results obtained through detailed analyses and evaluations, the research will aim to design, construct and test the requirements of efficient solar thermal collectors that are incorporated into existing hot water systems. Improvement opportunities for enhancing collector efficiency and incorporation into existing hot water systems will be explored.


The rapid development of AI technology in recent years has brought new possibilities to solve the dilemma in testing work. The use of deep neural networks, reinforcement learning and other technologies to create AI agents can respond to complex game strategies like high-level players, and assist QA to fully complete complex scene testing.
Through user data, AI can also simulate the real behavior of players at different levels, which can largely replace human players for large-scale testing, fully cover test scenarios, and shorten the feedback adjustment cycle. 

Not only that, due to the generalization of the neural network, AI requires only a few adjustments to deal with the changes brought about by the game upgrade, greatly reducing maintenance costs. And AI has features such as copyability, acceleration, and stable test results, which are impossible with traditional test methods.

\section{Preliminary Literature Review}
The advantages of automated testing are speed and scale, and automated testing with AI technology is no exception. In the following cases, testing can be performed in parallel in a distributed environment. The game itself runs in a container, and the AI ​​agent controls the operation of the game through the program interface, thereby simulating the user's behavior.


游戏行业有许多产品正在走向精品化，用户也越来越挑剔；游戏的制作过程、测试过程也正在走向细致化的道路。而在测试过程中引入的AI技术，正是一种把传统QA测试中的不可能变为可能，并且极大提高生产效率的手段。

除此之外，新的AI技术也在渗透到传统基于行为树的游戏AI中，使NPC、队友、对手更加智能。长久以来几乎没有太大变化的游戏AI体系，在人工智能大潮的冲击下有了无限的可能性。AI在游戏中的使命不再仅限于保证游戏体验，在模拟人类、增强游戏可玩性、提高游戏设计效率方向上有了更多的要求。相信除了IP因素之外，游戏内容的智能化也将是人工智能时代游戏领域的新热点。


\section{Methodology}

\bibliography{ref}

\end{document}
