% ************************** Thesis Acknowledgements **************************

\begin{acknowledgments}
    %经过两年的硕士研究生阶段的学习，在论文完成之际，我真诚地向曾经帮助过我的老师、学院领导、辅导员、同学以及朋友们表示诚挚的谢意。

    %首先，我要特别感谢我的导师王志锋教授，他在我完成平常的科研任务的过程中，给予了耐心细致的指导和极大的帮助。在本文的选题、构思、实验仿真和论文撰写过程中，也提出了相当多有益而启发性的建议。最终使我的论文得到了不断的完善。这都多亏了王老师的辛勤指导和教诲。

    %然后，我要感谢学院所有的领导和老师，他们在我的硕士阶段的工作和学习过程中，提出了相当多宝贵的建议，让我的内心得到了锤炼，对此我充满了感激。这对于我今后的职业生涯，无疑是不可多得的宝贵财富。

    %另外还要感谢三年来和我一起走过研究学习生涯的全体同学和朋友们，在学习中我们相互帮助，互相激励和关心。感谢他们的友情和支持。


    %%Write the acknowledgments here ...
    After two years of study at the postgraduate level, when the thesis is completed, I sincerely express my sincere thanks to the teachers, college leaders, counsellors, classmates and friends who have helped me.

    First of all, I would like to thank my supervisor, Professor Wang, who gave me patient and meticulous guidance and great help in completing my usual scientific research tasks. In the process of topic selection, conception, experimental simulation and thesis writing, many useful and enlightening suggestions were also put forward. Finally, my thesis has been continuously improved. This is all thanks to the stern guidance and teaching of Teacher Wang.

    Then, I would like to thank all the leaders and teachers of the college. They put forward many valuable suggestions during my master's work and study process, which tempered my heart. I am full of gratitude for this. This is undoubtedly a rare and valuable asset for my future career.

    I also want to thank all my classmates and friends who have gone through the research and study career in the past three years. We have helped each other, inspired and cared for each other in our studies. Thank them for their friendship and support.

\end{acknowledgments}
