\documentclass[12pt]{article}%


\begin{document}

\title{Solution 1}
\author{Wangzhihui Mei \\ 2019124044 6603385}
\date{}
\maketitle

\section*{Task 1}
\subsection*{(1)}
The functional dependencies are:

\noindent For relational schema \textbf{Employee}:

e\# $\rightarrow$ name 

e\# $\rightarrow$ dob

e\# $\rightarrow$ dname

e\# $\rightarrow$ Supervisor\#

\noindent For relational schema \textbf{Department}:

e\# $\rightarrow$ dname

dname $\rightarrow$ manager, msdate

e\# $\rightarrow$ manager, msdate

\noindent For relational schema \textbf{DeptLocation}:

dname $\rightarrow$ manager

dname, address $\rightarrow$ manager

\noindent In schema Employee, (e\#)$^+$=\{e\#, name, dob, dname, Supervisor\}, (e\#) is the minimal key of Employee. 
Every nonprime attribute in Employee is fully functionally dependent on e\#, so Employee is in the 2NF.
No nonprime attribute of Employee is transitively dependent on the primary key e\#, so Employee is in the 3NF.
No other attribute X satisfy X$\rightarrow$ e\#, so Employee is in the BCNF, the highest normal form valid of Employee is BCNF.

\noindent In original schema Department, (e\#)$^+$=\{e\#, dname, manager, msdate\}, (e\#) is the minimal key of Department. Every nonprime attribute in Employee is fully functionally dependent on e\#, Department is in 2NF. 
But We get (e\#)$\rightarrow$(dname)$\rightarrow$(manager, msdate), so (manager, msdate) is transitively dependent on the primary key e\#. To make Department schema in BCNF, we should remove attribute e\# from Department, as the attribute is in Employee schema. The modified Department schema has the minimal key (dname), and it is in BCNF.

\noindent In original schema DeptLocation, (dname, address)$^+$=\{dname, address, manager\}, (dname, address) is the minimal key of DeptLocation. Nonprime attribute manager is not fully functionally dependent on (dname, address) as dname$\rightarrow$manager, so DeptLocation is not in 2NF. The hightest normal form valid for DeptLocation is 1NF. To make DeptLocation in BCNF, we should remove manager attribute which is already in Department schema. So the (dname, address) will be the only attribute of DeptLocation, it is in BCNF. 



\clearpage

\end{document}